Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-11 ms.tex
fixed TDE section

The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
time, $t_{\rm grow} = M_{\bullet}/\dot{M}$, for each accretion rate
shown in the top panel.  For black holes accreting steadily given the
stellar wind heating associated with the average star formation
history of their galaxies, we see that $t_{\rm grow}$ exceeds the
Hubble time by 1$-$3 orders of magnitude across all black hole masses.
Steady accretion therefore cannot explain the growth of low mass black
holes, a fact which is not surprising given that approximately half of
this growth occurs in AGN radiating within 10 per cent of their
Eddington rate (\citealt{Heckman+04}).  Such high accretion rates
likely instead require an source of gas external to the nuclear
region, triggered either by galaxy mergers associated with the
hierachical growth of structure or thermal instabilities on larger,
galactic scales (e.g.~\citealt{Ciotti+10}).

\citet{Kauffmann&Heckman09} find that the growth of low mass black
holes is dominated by young stellar bulges which have a log normal
distribution of Eddington ratios peaked at $\Mdot/\MdotEdd\sim
0.01$. The distribution is insensitive to galaxy properties which
suggestes that it is set by feedback from the black hole rather than
from the gas supply in the nucleus.

That the growth time associated with thermally-unstable accretion
(yellow line) exceeds the Hubble time across all SMBH masses
highlights the fact that signifcant black hole growth in the local
universe cannot result from thermally-stable steady accretion of gas
lost from the surrounding stellar population.

Gas blow-out by SN Ia cannot prevent the growth of low-mass black
holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
Ia heating (green lines), although Ia heating could play in principle
a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black
holes, again depending on the efficiency of Ia heating.

@@

Our results also have implications for the environments encountered by
relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
J1644+57 (\citealt{Bloom+11}), we predict gas densities of a $n
\sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating
rates within the physically expected range $v_{\rm w} \sim 500-1000$
km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values are within the
range estimated by modeling the radioa afterglow of {\it Swift}
J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}).  In fact, the
flattening of the density profile inferred by \citet{BergerZauderer+:2012a} on
radii scales $r \gtrsim 0.4$ pc (their Fig.~6) looks similar to that
seen in our calculations of the gas density profile for core galaxies
(Fig.~\ref{fig:profiles}, solid line).  The CNM density of the host of
{\it Swift} J1644+57 was a factor of 30 times lower than that inferred
by \citet{Quataert:2004a} for SgrA*, a fact we attribute to...{\bf
  BDM: whats going on?}  The implications of our models for CNM
profiles for the diversity of radio emission from TDE jets will be
explored further in future work.

>>>>

The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
time, $t_{\rm grow} = M_{\bullet}/\dot{M}$, for each accretion rate
shown in the top panel.  For black holes accreting steadily given the
stellar wind heating associated with the average star formation
history of their galaxies, we see that $t_{\rm grow}$ exceeds the
Hubble time by 1$-$3 orders of magnitude across all black hole masses.
Steady accretion therefore cannot explain the growth of low mass black
holes, a fact which is not surprising given that approximately half of
this growth occurs in AGN radiating within 10 per cent of their
Eddington rate (\citealt{Heckman+04}).  Such high accretion rates
likely instead require an source of gas external to the nuclear
region, triggered either by galaxy mergers associated with the
hierachical growth of structure or thermal instabilities on larger,
galactic scales (e.g.~\citealt{Ciotti+10}).  In support of this, \citet{Kauffmann&Heckman09} find that the growth of low mass black holes is dominated by young stellar bulges which have a log normal
distribution of Eddington ratios peaked at $\Mdot/\MdotEdd\sim
0.01$. That this distribution is insensitive to galaxy properties suggestes that it is set by SMBH feedback instead of the nuclear gas supply.

That the growth time associated with thermally-unstable accretion
(yellow line) exceeds the Hubble time across all SMBH masses
highlights the fact that signifcant black hole growth in the local
universe cannot result from thermally-stable steady accretion of gas
lost from the surrounding stellar population studied in this paper.  Gas blow-out by SN Ia cannot prevent the growth of low-mass black holes, as indicated by the low growth times $\ll t_{\rm h}$ allowed by
Ia heating (green lines), although Ia heating could play in principle a role in capping the growth rate of $\gtrsim 10^{8}M_{\odot}$ black holes, again depending on the efficiency of Ia heating and whether the galaxy is a core or cusp.

@@

Our results also have implications for the environments encountered by
relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
J1644+57 (\citealt{Bloom+11}), we predict gas densities of a $n
\sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating
rates within the physically expected range $v_{\rm w} \sim 500-1000$
km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values are within the
range estimated by modeling the radio afterglow of {\it Swift}
J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}).

\citet{BergerZauderer+:2012a}  infer a flattening of the gas density profile on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks qualitiatively similar to that the density profile we predict for core galaxies (Fig.~\ref{fig:profiles}, solid line).  Their inferred  gas profile also shows a break at radii $\sim 0.6$ pc, which in our model corresponds to the break radius of the galaxy and hence would imply a SMBH mass of TINY accroding to the mean relationship from the \citet{Lauer+Faber:2007a} sample.  More detailed models for the environment, and the implications of our models for CNM profiles for the diversity of radio emission from TDE jets, will be
explored further in future work.
